\documentclass[letterpaper,10pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage[usenames,dvipsnames]{color}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{ragged2e}
\input{glyphtounicode}

% font options
\usepackage{newpxtext}
\linespread{1.0}
\usepackage[T1]{fontenc}

\pagestyle{fancy}
\fancyhf{}  % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% adjust margins
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.6in}
\addtolength{\textheight}{1.2in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}
\setlength{\footskip}{5pt}

% sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule\vspace{-6pt}]

% ensure that generate pdf is machine readable/ATS parsable
\pdfgentounicode=1

% custom commands
\newcommand{\cvitem}[1]{
  \item\small{
    {#1\vspace{-2pt}}
  }
}

\newcommand{\cvheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \small#3 & \small #4 \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\cvheadingstart}{\begin{itemize}[leftmargin=0in, label={}]}
\newcommand{\cvheadingend}{\end{itemize}}
\newcommand{\cvitemstart}{\begin{itemize}[label=\textopenbullet]}
\newcommand{\cvitemend}{\end{itemize}\vspace{-5pt}}

\renewcommand\labelitemii{$\vcenter{\hbox{\footnotesize$\bullet$}}$}

\begin{document}

% contact information
\begin{center}
  \textbf{\LARGE\scshape Nguyen Dinh Loc} \\
  \vspace{1pt}\small
  \href{mailto:locgopro005@gmail.com}{locgopro005@gmail.com}
  $\ \diamond\ $ 
  +84 987 395 459
  $\ \diamond\ $
  \href{https://huggingface.co/bunbohue}{HuggingFace}
  $\ \diamond\ $
  \href{https://www.linkedin.com/in/gin-tonic/}{LinkedIn}
\end{center}

\section{Professional Experience}
\cvheadingstart
  \cvheading
    {eUp}{Hanoi, Vietnam}
    {AI Engineer}{11/2024 - Present}
  \cvitemstart
    \cvitem{\textbf{Todaii Japanese}: Fine-tuned GPT-4 with supervised fine-tuning (SFT) to rewrite NHK articles by JLPT level; built prompt workflows and evaluation loops with the OpenAI API.}
    \cvitem{\textbf{Mazii Dictionary}: Implemented a Cached Augmented Generation (CAG) pipeline for personalized Japanese dictionary lookup using GPT-4.1-mini, LangChain, and LangGraph.}
    \cvitem{\textbf{Mazii Speech}: Built real-time Japanese TTS streaming and anime-style voice cloning with KokoroTTS, VITS, HuBERT, and RMVPE; optimized inference with INT8 quantization, ONNX and LRU caching.}
    \cvitem{\textbf{Mazii Foundation Model}: Post-trained (DFT) a lightweight model (Gemma 4 MoE) to Japanese foundation model for vocabulary, kanji, grammar, and general knowledge base; Optimized inference with 4-bit quantization (NVFP4); Optimized serving with KV-cache utilization, Radix Attention, and Continuous Batching.}
    \cvitem{\textbf{HeyChina AI}: Built personalized AI characters for Chinese learners; applied post-training (DPO) in GLM-4.7-Flash. Optimized inference with 8-bit quantization (FP8). Deploy to production using LangChain, and LangGraph.}
  \cvitemend

  \cvheading
    {Panasonic R\&D Center Vietnam}{Hanoi, Vietnam}
    {AI Engineer}{07/2024 - 10/2024}
  \cvitemstart
    \cvitem{Researched and developed the CTO Translation Tool, a meeting-audio assistant for transcription, translation, and meeting notes.}
    \cvitem{Integrated ASR with speaker diarization, OpenAI API workflows, and a Gradio interface.}
  \cvitemend

  \cvheading
    {VinBigData Institute}{Hanoi, Vietnam}
    {Teaching Assistant}{07/2024 - 09/2024}
  \cvitemstart
    \cvitem{Supported the NLP course for the VinBDI AI Engineer Training Program, including lectures, exercises, and student guidance.}
  \cvitemend

  \cvheading
    {Kaopiz Software Co., Ltd.}{Hanoi, Vietnam}
    {AI Engineer}{06/2023 - 06/2024}
  \cvitemstart
    \cvitem{Developed Japanese OCR modules for text detection and recognition using RCNN, CRNN, and PaddleOCR.}
    \cvitem{Optimized model runtime with ONNX, TensorFlow Lite, and OpenVINO for Intel CPU deployment.}
    \cvitem{Built an image-matching service for FOCUS Media using image embeddings, compression, and augmentation; containerized the service with Docker and achieved 93.64\% search accuracy.}
  \cvitemend

  \cvheading
    {Intelligent Software Engineering Lab - BKAI}{Hanoi, Vietnam}
    {Research Assistant}{03/2022 - 09/2023}
  \cvitemstart
    \cvitem{Researched AI-assisted software engineering across requirements engineering and debugging.}
    \cvitem{Explored ML methods for representing software artifacts and automating stages of the software development lifecycle.}
  \cvitemend
\cvheadingend

\section{Education}
\cvheadingstart
  \cvheading
    {Hanoi University of Science and Technology}{Hanoi, Vietnam}
    {Master's Student, Data Science Program, Information and Communication Technology}{10/2025 - Present}
  \cvheading
    {Hanoi University of Science and Technology}{Hanoi, Vietnam}
    {Engineer Degree, Information and Communication Technology (Very Good)}{09/2019 - 09/2024}
  \cvheading
    {High School for the Gifted - Vinh University}{Nghe An, Vietnam}
    {Physics, Very Good}{09/2016 - 09/2019}
\cvheadingend

\section{Technical Skills}
\cvheadingstart
\item
\cvitemstart
  \cvitem{\textbf{Programming}: Python, C++}
  \cvitem{\textbf{ML / DL}: Model Training - Evaluation - Compression, Deep Reinforcement Learning, Transformers-based, Encoder-Decoder models, Causal Language Modeling}
  \cvitem{\textbf{AI Agents}: Prompt Engineering, RAG, LangChain, LangGraph, OpenAI API}
  \cvitem{\textbf{AI Frameworks}: Hugging Face, PyTorch, TensorFlow, TensorFlow Lite}
  \cvitem{\textbf{AI Inference / Optimization}: ONNX, OpenVINO, SGLang, vLLM, TensorRT-LLM, KV cache optimization, Continuous Batching, Flash Attention}
  \cvitem{\textbf{Backend / Tools}: Docker, Flask API, FastAPI, Git, GitLab}
\cvitemend
\cvheadingend

\section{Additional}
\cvheadingstart
\item
\cvitemstart
  \cvitem{\textbf{Award}: Best Presentation Award, Summer School 2023 on Modern Machine Learning: ``Foundations and Applications'' (BKAI, NAVER, VinBigData)}
  \cvitem{\textbf{Languages}: English (TOEIC 885)}
\cvitemend
\cvheadingend

\end{document}
